Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/model.tex
fix typos

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. \asedit{The warm ensures that each firm has a meaningful reputation when competition starts.} Each firm's objective is to maximize its market share: the fraction of users who chose this firm.

>>>>

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. \asedit{The warm start ensures that each firm has a meaningful reputation when competition starts.} Each firm's objective is to maximize its market share: the fraction of users who chose this firm.
